Field-informed Reinforcement Learning for Learning Large-Scale Collective Tasks

### 2023-05-11 paper.tex
minor on intro

\begin{IEEEkeywords}
aggregate computing, Graph Neural Network, Cyber-Physical Swarms.
\end{IEEEkeywords}
%
\ga{Paper levels:
\begin{itemize}
  \item Distributed collective intelligence
  \item GNN and field coordination
  \item Spatial tracking
\end{itemize}
}
\section{Introduction}

@@

In this paper, we propose a novel approach combining aggregate computing~\cite{Beal2015Computer} with Graph Neural Networks~\cite{Zhou2020AIOpen} to focus on the relevant areas. We further combine this with reinforcement learning techniques to respond to changing conditions in the environment. 
%
This follow a novel trends in which high-level declarative programming language are mixed with machine learning technique in order to synthesise robust collective controllers~\cite{DBLP:conf/acsos/Aguzzi21,DBLP:conf/icdcs/AguzziCV22,DBLP:conf/coordination/AguzziCV22}.
%Specifically, we will show... \lukas{more info...}
Specifically, 
 our approach utilises aggregate computing to disseminate information by manipulating a computational field, 
 which is a distributed data structure that maps devices to information. 
 This field functions as a dynamic environment in which information is continuously updated and diffused throughout the system. 
 By leveraging this layer, we can build collective distributed intelligence using \ac{GNN},
  which uses the information in the field to determine the best action for a given task.
\ga{first draft, need a refinement}
The remainder of this paper is structured as follows. First, we introduce the relevant background and problem formulation in \Cref{sec:background}. Afterwards, we introduce our approach in \Cref{sec:approach}. \Cref{sec:eval} outlines the performed experiments and discusses the obtained results. Finally, we will present our conclusions in \Cref{sec:conclusion}.

>>>>

\begin{IEEEkeywords}
aggregate computing, Graph Neural Networks, and Cyber-Physical Swarms.
\end{IEEEkeywords}
%
\ga{Paper levels:
\begin{itemize}
  \item Distributed collective intelligence
  \item GNN and field coordination
  \item Spatial tracking
\end{itemize}
}
\section{Introduction}

@@

In this paper, we propose a novel approach combining aggregate computing~\cite{Beal2015Computer} with Graph Neural Networks~\cite{Zhou2020AIOpen} to focus on the relevant areas. We further combine this with reinforcement learning techniques to respond to changing conditions in the environment. 
%
This follows a novel trend in which high-level declarative programming languages are mixed with machine learning techniques in order to synthesise robust collective controllers~\cite{DBLP:conf/acsos/Aguzzi21,DBLP:conf/icdcs/AguzziCV22,DBLP:conf/coordination/AguzziCV22}.
%Specifically, we will show... \lukas{more info...}
Specifically, 
 our approach utilises aggregate computing to disseminate information by manipulating a computational field, 
 which is a distributed data structure that maps devices to information. 
 This field functions as a dynamic environment in which information is continuously updated and diffused throughout the system. 
 By leveraging this layer, we can build collective distributed intelligence using \ac{GNN},
  which uses the information in the field to determine the best action for a given task.
\ga{first draft, need a refinement}
The remainder of this paper is structured as follows. First, we introduce the relevant background and problem formulation in \Cref{sec:background}. Afterwards, we introduce our approach in \Cref{sec:approach}. \Cref{sec:eval} outlines the performed experiments and discusses the obtained results. Finally, we will present our conclusions in \Cref{sec:conclusion}.
